\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning, Reachability Analysis, and Network Flow

### 2024-12-12 response.tex

The simulation result, shown in Fig.4b, displays reachability regions as black ellipsoids, demonstrating empty intersections with Zones 2 and 3. Explicit constraints between reachability regions and obstacles are not activated, assuming basic obstacle avoidance capabilities in robots. The intersections between obstacles and ellipsoids, as observed between agent 3 and Zone 1, are deemed tolerable. All constraints are satisfied, and agents have effectively spread across the map for optimal exploration tasks.

1) Limitations:
Our solution demonstrates the potential of planning with reachability and co-observation to enhance the security of multi-agent systems. {\news However, two primary challenges need to be addressed. Firstly, achieving a co-observation and reachability-secured plan is not always feasible, particularly when obstacles or restricted regions separate the robots, preventing them from establishing co-observation schedules or finding reachability-secured paths. For example, agent 3 in~Fig.4b requires additional security measures to create secured reachability areas. Secondly, security requirements can impact overall system performance, as illustrated by the comparison between~Fig.2b and Fig.4b. The introduction of security constraints resulted in the top left corner remaining unexplored by any robots. This trade-off between security and system performance is particularly significant as system performance is a key factor in the decision of multi-agent system deployments. These challenges are further addressed in Section III, ensuring the effective integration of reachability and co-observation in securing multi-agent systems.}

\vspace{0.3cm}

\begin{cmt}{}{}
	Similarly, how the
	trajectories are broken down to multiple ellipsoid components are not
	clear, is it a design choice to make the constraints less conservative
	than setting a single ellipsoid with the start and goal point?
	\re 
	The reachability ellipsoids are designed to work in conjunction with the co-observation technique. Instead of using a single ellipsoid defined by the start and goal points, the ellipsoid are defined by smaller ellipsoids between two consecutive co-observation times. This approach ensures that the constraints are aligned with the co-observation schedule, reducing conservativeness while maintaining security guarantees. We also make modification to Definition 4 (Remark 1 in the original manuscript) to make this more clear.
\end{cmt}
\rv
{\news \setcounter{definition}{3}
 \begin{definition}\label{rmk:revised-security}
	A multi-robot trajectory is secured against plan-deviation attacks if there exists a co-observation plan such that the reachability region between each consecutive co-observation does not intersect with any forbidden regions.
\end{definition}}

@@

The simulation result, shown in Fig.4b, displays reachability regions as black ellipsoids, demonstrating empty intersections with Zones 2 and 3. Explicit constraints between reachability regions and obstacles are not activated, assuming basic obstacle avoidance capabilities in robots. The intersections between obstacles and ellipsoids, as observed between agent 3 and Zone 1, are deemed tolerable. All constraints are satisfied, and agents have effectively spread across the map for optimal exploration tasks.

1) Limitations:
Our solution demonstrates the potential of planning with reachability and co-observation to enhance the security of multi-agent systems. {\news However, two primary challenges need to be addressed. Firstly, achieving a co-observation and reachability-secured plan is not always feasible, particularly when obstacles or restricted regions separate the robots, preventing them from establishing co-observation schedules or finding reachability-secured paths. For example, agent 3 in~Fig.4b requires additional security measures to create secured reachability areas. Secondly, security requirements can impact overall system performance, as illustrated by the comparison between~Fig.2b and Fig.4b. The introduction of security constraints resulted in the top left corner remaining unexplored by any robots. This trade-off between security and system performance is particularly significant as system performance is a key factor in the decision of multi-agent system deployments. These challenges are further addressed in Section III, ensuring the effective integration of reachability and co-observation in securing multi-agent systems.}

\begin{cmt}{}{}
	p 8 - A heuristic approach is provided (Algorithm 1); Is it
	almost impossible for the reader to decipher this algorithm without any
	explanations in words.
\re	We have replaced the algorithm with more detailed and understandable prose to improve readability and make the approach easier to follow.
\end{cmt}
\rv {\news We begin by adding the start and end locations $(q_{p}(t_0),t_0)$, $(q_{p}(t_2),t_2)$ to $V_{p}$, with $t_{0}=0$, $t_2=T$ as \emph{start} and \emph{end verticies}. Then, we search for the largest $t_{1} \in \{t_{0}+1, \dots ,t_{2}\}$ such that the reachability ellipsoid between $q_{p}(t_{0})$ and $q_{p}(t_{1})$ has no overlap with any of the forbidden areas, i.e. $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1})\intersect F = \emptyset$. Then $(q_{p}(t_{1}),t_1)$ is added to $V_{p}$. Simultaneously, we search backward to find $q_{p}(t_{3})$ with the smallest $t_{3}\in \{t_{1},\dots,t_{2}-1\} $ that meets the reachability requirement $\mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}),t_{2},t_{3}) \intersect F = \emptyset$. Then $(q_{p}(t_{3}),t_3)$ is added to $V_{p}$. Finally, we set $t_{0}\leftarrow t_{1}$, $t_{2}\leftarrow t_{3}$ and repeat the same process. The search is stopped when $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \intersect F = \emptyset$ or $t_{0}>t_{2}$. A toy example is shown in \cref{fig:checkpoint-generate}. }

### 2024-12-12 paper.tex
last notes

\section{Introduction}\label{sec:introduction}
Multi-robot systems (MRS) have found wide applications in various fields. While offering numerous advantages, the distributed nature and dependence on network communication render the MRS vulnerable to cyber threats, such as unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}. This paper addresses a specific scenario in which robots are compromised by attackers and directed to \emph{forbidden regions}, which may contain security-sensitive equipment or human workers. Such countering deliberate deviations, termed \emph{plan-deviation attacks}, are identified and addressed in previous studies \cite{wardega2019resilience, wardega2023byzantine, wardega2023hola, yang2021multi, yang2020multi}. As a security measure, we utilized the onboard sensing capabilities of the robots to perform inter-robot co-observations and check for unusual behavior. These mutual observation establish a co-observation schedule alongside the path, ensuring that any attempts by a compromised robot to violate safety constraints (such as transgressing forbidden regions) would break the observation plan and be promptly detected.

A preliminary version of the paper is presented in \cite{yang2020multi,yang2021multi}. Extending the grid-world solution from \cite{wardega2019resilience} to continuous configuration spaces, we incorporate the co-observation planning as constraints in \new{the alternating direction method of multipliers (ADMM)}-based trajectory optimization solver to accommodate for more flexible objectives. In this paper, we incorporate additional reachability analysis during the planning phase, incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}, as a novel perspective to the existing literature. This approach enforces an empty intersection between forbidden regions and the reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots. We utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint. We present a mathematical formulation of reachability regions compatible with the solver in \cite{yang2020multi} as a spatio-temporal constraint.

However, such plans are not guaranteed to exist, and the secured trajectory always comes at the cost of overall system performance. As an extension of the previous works \cite{yang2020multi,yang2021multi}, we also address the feasibility and optimality challenges. For a MRS with unsecured optimal trajectories (without security constraints), we introduce redundant robots and formed them into \emph{sub-teams} with the original ones. These redundant robots are assigned to establish additional co-observations, termed \emph{cross-trajectory co-observations}, within and across different sub-teams. The proposed algorithm focuses on the movement plans for the additional robots, distinct from those dedicated to task objectives, indicating when they should stay with their current sub-team and when they should deviate to join another. This strategy allows sub-teams to preserve the optimal unsecured trajectories (as illustrated in \cref{fig:cross-traj-comparison-set}) without requiring the entire \emph{sub-team} to maintain close proximity to other teams during co-observation events. The cross-trajectory co-observation problem is transformed as a \new{Multi-Agent Pathfinding (MAPF)} problem on roadmap (represented as directed graph) and solved as a network flow problem \cite{yu2013multi}.

@@

\begin{example}\label{example:map_exploration}
\new{Robots are tasked with navigating an unknown task space to collecte sensory data to reconstruct a field (as illustrated in~\cref{fig:illustration}). The task space is modeled as a grid, where each grid point has an associated value tracked by a Kalman Filter (KF) \cite{anderson2012optimal}. The KF estimates uncertainty at each point through its covariance $P_j$ updated based on the measurements taken by robots along the trajectory $\vq$. Measurement quality, modeled by a Gaussian radial basis function, decreases with distance from the robot. The optimization objective $\varPhi(\vq)=\max_j P_j(\vq)$ is to minimize the maximum uncertainty in reconstructing the field (detailed in \cite{yang2020multi}). }
\end{example}
\begin{figure}
  \centering
  \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth,, trim = 0.3cm 1.3cm 0.3cm 2cm,valign=c]{illustration figure_1}} 
  \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 0.3cm 1.3cm 0.3cm 2cm, valign=c]{SecurityBreak_v2}}
  % \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
  \caption{\new{(\ref{fig:illustration}) Illustration of a 3 robot map exploration task case. (\ref{fig:SecurityBreak}) The unsecured trajectory design optimized for a map exploration task. Potential security breaches, indicated by red dashed lines, highlight paths that could allow unauthorized access to forbidden regions.}}
\end{figure}

{\news Ideally, robots are expected to spread out in a boustrophedon pattern to efficiently explore the task space, optimizing coverage and minimizing reconstruction uncertainty (\cref{fig:SecurityBreak}). To address potential threats, we adopt the \emph{physical masquerade attacks} framework from~\cite{wardega2019resilience}, where a compromised insider (robot) masquerading as a properly functioning robot, attempting to gain access to unauthorized locations without detection. The attacker leverages full knowledge of the motion plan and exploits the compromised robot to provide false self-reports to the central entity (CE). These malicious deviations remain undetected as long as the self-reports from uncompromised robots align with the motion plan. The corresponding security requirement can then be formally defined as:}
\begin{definition}\label{def:secured-plan}
  A multi-robot trajectory plan is \new{secured against} plan-deviation attacks if it \new{ensures} that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots. 
\end{definition}

@@

The update steps of the algorithm are then derived as \cite{Boyd2011}:
\begin{subequations}\label{eq:ADMMupdate}
	\begin{align}
		\vq^{k+1}&:=\argmin_\vq(\varPhi(\vq^k) +\frac{\rho}{2}\norm{D(\vq)-\vz^k+\vu^k}_2^2),\label{eq:admm-mod-update-q}\\
		\vz^{k+1}&:=\Pi_\mathcal{Z}(D(\vq^{k+1})+\vu^k), \label{eq:z-update} \\
		\vu^{k+1}&:=\vu^k+D(\vq^{k+1})-\vz^{k+1}, \label{eq:u-update}
	\end{align}
\end{subequations}
where $\Pi_\mathcal{Z}$ is the new projection function to the modified constraint set $\mathcal{Z}$, $\vu$ represents a scaled dual variable that, intuitively, accumulates the sum of primal residuals
\begin{equation}\label{eq:primal-residual}
	\vr^{k}=D(\vq^{k+1})-\vz^{k+1}.
\end{equation}
Checking the primal residuals alongside the dual residuals 
\begin{equation}\label{eq:dual-residual}
	\vs^{k}=-\rho(\vz^{k}-\vz^{k-1})
\end{equation}
after each iteration, the steps are reiterated until convergence when the primal and dual residuals are small, or divergence when primal and dual residuals remain large after a fixed number of iterations.
{\news
\begin{remark}
In practical application, \eqref{eq:admm-mod-update-q} is solved iteratively via a nonlinear optimization solver like \emph{fmincon}. The gradients of the constraint functions, derived later, is used to enhance solver efficiency and accuracy. Meanwhile, \eqref{eq:z-update} and~\eqref{eq:u-update} have closed form solutions.
\end{remark}
}
% \rtron{Maybe state here that (9a) is solved iteratively, while (9b) and (9c) are closed-form.}

@@

We employ the \new{attack-proof MAPF(APMAPF)} solver \cite{wardega2019resilience} on an 8 by 8 grid world with a similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.\ref{fig:Grid-example-application}). This result is transformed to a continuous configuration space and serves as the initial trajectory input for the ADMM solver with an additional task function targeting the map exploration task. Co-observation schedules are set up using the APMAPF algorithm for two forbidden regions. Reachability constraints are added to ensure an empty intersection between all robots' reachability regions during co-observations and the forbidden regions. {\news It is important to emphasize that an APMAPF solution does not guarantee existence, nor does it ensure a successful transition to the continuous configuration space. In this case, while an APMAPF solution may be found, the secured, attack-proof solution becomes infeasible in the continuous setting because the robots' mobility is no longer restricted to adjacent grids. Additional security measures, such as stationary security cameras or surveillance robots, need to be incorporated. For instance, in this scenario, we deploy a security camera as additional security measure to observe agent 3 at time $8$ to ensure security.}

@@

%Based on the schedule, reachability for agent 1 in-between the scheduled co-observations are constrained. Notice that additional checkpoint (i.e. stationary security camera) need to be incorporated in order to generated an attack-proof solution. Additional solutions to avoid these checkpoints will be discussed in \cref{sec:cross-trajectory}.  
%The result of the simulation is shown in Fig.~\ref{fig:ReachabilitySimulation}. The reachability regions are shown as black ellipsoids, and we can show that all of them have empty intersections with Zone 2 and 3. Notice that no explicit constraints have been enabled between reachability regions and obstacles, because we assume that robots have the basic obstacle avoidance capability and can not go through any hard obstacles. Therefore, the intersections between obstacles and ellipsoids, i.e. the case here between agent 3 and zone 1, are tolerable. All constraints have been satisfied and, to the best of their capability, agents have spread out across the map to perform the best possible exploration task. 
\begin{figure}
  \centering
  % \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
  \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth,trim =0cm 0cm 0cm 0cm, clip,valign=t]{Grid_world}}
  % \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth,valign=c]{SecurityBreak_v2}}
  \subfloat[Securd result \label{fig:ReachabilitySimulation}]{\includegraphics[width=0.52\linewidth,trim =2cm 1.5cm 2cm 1.5cm, clip,valign=t]{FinalResult}}
  \caption{{\news Trajectory design a three-robot system based on the grid world result. Zone 1 is an obstacle, Zone 2 and Zone 3 are forbidden regions. (\ref{fig:Grid-example-application}) Result of the APMAPF algorithm in 8$\times$8 grid-world without map exploring objective. (\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation generated by APMAPF and additional reachability constraints.}}
  \label{fig:example-application}
\end{figure}

@@

{\news We begin by adding the start and end locations $(q_{p}(t_0),t_0)$, $(q_{p}(t_2),t_2)$ to $V_{p}$, with $t_{0}=0$, $t_2=T$ as \emph{start} and \emph{end verticies}. Then, we search for the largest $t_{1} \in \{t_{0}+1, \dots ,t_{2}\}$ such that the reachability ellipsoid between $q_{p}(t_{0})$ and $q_{p}(t_{1})$ has no overlap with any of the forbidden areas, i.e. $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1})\intersect F = \emptyset$. Then $(q_{p}(t_{1}),t_1)$ is added to $V_{p}$. Simultaneously, we search backward to find $q_{p}(t_{3})$ with the smallest $t_{3}\in \{t_{1},\dots,t_{2}-1\} $ that meets the reachability requirement $\mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}),t_{2},t_{3}) \intersect F = \emptyset$. Then $(q_{p}(t_{3}),t_3)$ is added to $V_{p}$. Finally, we set $t_{0}\leftarrow t_{1}$, $t_{2}\leftarrow t_{3}$ and repeat the same process. The search is stopped when $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \intersect F = \emptyset$ or $t_{0}>t_{2}$. A toy example is shown in \cref{fig:checkpoint-generate}. }

>>>>

\section{Introduction}\label{sec:introduction}
Multi-robot systems (MRS) have found wide applications in various fields. Although offering numerous advantages, the distributed nature and dependence on network communication make the MRS vulnerable to cyber threats, such as unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}. This paper addresses a specific scenario in which robots are compromised by \new{physically masquerading} attackers and directed toward \emph{forbidden regions}, which may contain security-sensitive equipment or human workers. {\news A countermeasure to these \emph{plan-deviation attacks} \cite{wardega2019resilience, wardega2023byzantine, wardega2023hola} is to use the onboard sensing capabilities of the robots themselves to perform inter-robot \emph{co-observations} and detect unusual behavior.
These mutual observations establish a \emph{co-observation schedule} alongside the planned path, ensuring that any attempts by a compromised robot to violate safety constraints (such as transgressing into forbidden regions) would break the observation plan and be promptly detected.}

A preliminary version of this approach is presented in \cite{yang2020multi,yang2021multi}. That work extended the grid-world solution from \cite{wardega2019resilience} to continuous configuration spaces, and incorporated the co-observation planning as constraints in \new{the alternating direction method of multipliers (ADMM)-based trajectory optimization solver to accommodate for more flexible objectives. However, such plans are not guaranteed to exist, and the secured trajectory always comes at the cost of overall system performance. As an extension of the previous works \cite{yang2020multi,yang2021multi}, we introduce reachability analysis and network flow to the security problem to find a balance between security and performance.}
In this paper, we incorporate an additional reachability analysis during the planning phase, incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}, as a novel perspective to the existing literature. This approach enforces an empty intersection between forbidden regions and the reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots. We utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint. We present a mathematical formulation of the reachability regions \new{as spatio-temporal constraints} compatible with the solver in \cite{yang2020multi}. 
 we also address the feasibility and optimality challenges. For a MRS with unsecured optimal trajectories (without security constraints), we introduce redundant robots and formed them into \emph{sub-teams} with the original ones. These redundant robots are assigned to establish additional co-observations, termed \emph{cross-trajectory co-observations}, within and across different sub-teams. The proposed algorithm focuses on the movement plans for the additional robots, distinct from those dedicated to task objectives, indicating when they should stay with their current sub-team and when they should deviate to join another. This strategy allows sub-teams to preserve the optimal unsecured trajectories (as illustrated in \cref{fig:cross-traj-comparison-set}) without requiring the entire \emph{sub-team} to maintain close proximity to other teams during co-observation events. The cross-trajectory co-observation problem is transformed as a \new{Multi-Agent Pathfinding (MAPF)} problem on roadmap (represented as directed graph) and solved as a network flow problem \cite{yu2013multi}.

@@

\begin{example}\label{example:map_exploration}
\new{Robots are tasked with navigating an unknown task space to collect sensory data and reconstruct a field (as illustrated in~\cref{fig:illustration}). The task space is modeled as a grid, where each grid point has an associated value tracked by a Kalman Filter (KF) \cite{anderson2012optimal}. The KF estimates uncertainty at each point through its covariance $P_j$ updated based on the measurements taken by robots along the trajectory $\vq$. Measurement quality, modeled by a Gaussian radial basis function, decreases with distance from the robot. The optimization objective $\varPhi(\vq)=\max_j P_j(\vq)$ is to minimize the maximum uncertainty in reconstructing the field (detailed in \cite{yang2020multi}). }
\end{example}
\begin{figure}
  \centering
  \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth,, trim = 0.3cm 1.3cm 0.3cm 2cm,valign=c]{illustration figure_1}} 
  \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 0.3cm 1.3cm 0.3cm 2cm, valign=c]{SecurityBreak_v2}}
  % \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
  \caption{\new{(\ref{fig:illustration}) Illustration of a 3 robot map exploration task case. (\ref{fig:SecurityBreak}) The unsecured trajectory design optimized for a map exploration task. Potential security breaches, indicated by red dashed lines, highlight paths that could allow unauthorized access to forbidden regions.}}
\end{figure}

{\news Ideally, robots are expected to spread out in a Boustrophedon pattern to efficiently explore the task space, optimizing coverage, and minimizing reconstruction uncertainty (\cref{fig:SecurityBreak}). However, we consider the possibility of threats following the \emph{physical masquerade attack} model \cite{wardega2019resilience}, where a compromised insider (robot) masquerading as properly functioning agent, attempts to gain access to unauthorized locations without detection. The attacker leverages full knowledge of the motion plan and exploits the compromised robot to provide false self-reports to the central entity (CE). These malicious deviations remain undetected as long as observations from uncompromised robots align with the motion plan. The corresponding security requirement can then be formally defined as:}
\begin{definition}\label{def:secured-plan}
  A multi-robot trajectory plan is \new{secured against} plan-deviation attacks if it \new{ensures} that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots. 
\end{definition}

@@

The update steps of the algorithm are then derived as \cite{Boyd2011}:
\begin{subequations}\label{eq:ADMMupdate}
	\begin{align}
		\vq^{k+1}&:=\argmin_\vq(\varPhi(\vq^k) +\frac{\rho}{2}\norm{D(\vq)-\vz^k+\vu^k}_2^2),\label{eq:admm-mod-update-q}\\
		\vz^{k+1}&:=\Pi_\mathcal{Z}(D(\vq^{k+1})+\vu^k), \label{eq:z-update} \\
		\vu^{k+1}&:=\vu^k+D(\vq^{k+1})-\vz^{k+1}, \label{eq:u-update}
	\end{align}
\end{subequations}
where $\Pi_\mathcal{Z}$ is the new projection function to the modified constraint set $\mathcal{Z}$, $\vu$ represents a scaled dual variable that, intuitively, accumulates the sum of primal residuals
\begin{equation}\label{eq:primal-residual}
	\vr^{k}=D(\vq^{k+1})-\vz^{k+1}.
\end{equation}
Checking the primal residuals alongside the dual residuals 
\begin{equation}\label{eq:dual-residual}
	\vs^{k}=-\rho(\vz^{k}-\vz^{k-1})
\end{equation}
after each iteration, the steps are reiterated until convergence when the primal and dual residuals are small, or divergence when primal and dual residuals remain large after a fixed number of iterations.
{\news
\begin{remark}
In practical application, \eqref{eq:admm-mod-update-q} is solved iteratively via a nonlinear optimization solver such as \emph{fmincon} \rtron{Add ref}. The use of explicit gradients of the constraint functions (derived below) greatly enhances the solver's efficiency and accuracy (with respect to the use of numericall differentiation). At the same time, \eqref{eq:z-update} and~\eqref{eq:u-update} have closed form solutions.
\end{remark}
}
% \rtron{Maybe state here that (9a) is solved iteratively, while (9b) and (9c) are closed-form.}

@@

We employ the \new{Attack-Proof MAPF (APMAPF)} solver \cite{wardega2019resilience} on an 8 by 8 grid world with a similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.\ref{fig:Grid-example-application}). This result is transformed to a continuous configuration space and serves as the initial trajectory input for the ADMM solver with an additional task function targeting the map exploration task. Co-observation schedules are set up using the APMAPF algorithm for two forbidden regions. Reachability constraints are added to ensure an empty intersection between all robots' reachability regions during co-observations and the forbidden regions. {\news It is important to emphasize that an APMAPF solution does not guarantee existence, nor does it ensure a successful transition to the continuous configuration space. In this case, while an APMAPF solution may be found, the secured, attack-proof solution becomes infeasible in the continuous setting because the robots' mobility is no longer restricted to adjacent grids. Additional security measures, such as stationary security cameras or surveillance robots, need to be incorporated. For instance, in this scenario, we deploy a security camera as additional security measure to observe agent 3 at time $8$ to ensure security.}

@@

%Based on the schedule, reachability for agent 1 in-between the scheduled co-observations are constrained. Notice that additional checkpoint (i.e. stationary security camera) need to be incorporated in order to generated an attack-proof solution. Additional solutions to avoid these checkpoints will be discussed in \cref{sec:cross-trajectory}.  
%The result of the simulation is shown in Fig.~\ref{fig:ReachabilitySimulation}. The reachability regions are shown as black ellipsoids, and we can show that all of them have empty intersections with Zone 2 and 3. Notice that no explicit constraints have been enabled between reachability regions and obstacles, because we assume that robots have the basic obstacle avoidance capability and can not go through any hard obstacles. Therefore, the intersections between obstacles and ellipsoids, i.e. the case here between agent 3 and zone 1, are tolerable. All constraints have been satisfied and, to the best of their capability, agents have spread out across the map to perform the best possible exploration task. 
\begin{figure}
  \centering
  % \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
  \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[height = 0.47\linewidth,trim =0cm 0cm 0cm 0cm, clip,valign=t]{Grid_world}}
  % \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth,valign=c]{SecurityBreak_v2}}
  \subfloat[Secured result \label{fig:ReachabilitySimulation}]{\includegraphics[height=0.47\linewidth,trim =2cm 1.8cm 2cm 1.5cm, clip,valign=t]{FinalResult}}
  \caption{{\news Trajectory design a three-robot system based on the grid world result. Zone 1 is an obstacle, Zone 2 and Zone 3 are forbidden regions. (\ref{fig:Grid-example-application}) Result of the APMAPF algorithm in $8\times8$ grid-world without the map exploring objective. (\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation generated by APMAPF and additional reachability constraints.}}
  \label{fig:example-application}
\end{figure}

@@

{\news \rtron{Use enumerate} We begin by adding the start and end locations $(q_{p}(t_0),t_0)$, $(q_{p}(t_2),t_2)$ to $V_{p}$, with $t_{0}=0$, $t_2=T$ as \emph{start} and \emph{end verticies}. Then, we search for the largest $t_{1} \in \{t_{0}+1, \dots ,t_{2}\}$ such that the reachability ellipsoid between $q_{p}(t_{0})$ and $q_{p}(t_{1})$ has no overlap with any of the forbidden areas, i.e. $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1})\intersect F = \emptyset$. Then $(q_{p}(t_{1}),t_1)$ is added to $V_{p}$. Simultaneously, we search backward to find $q_{p}(t_{3})$ with the smallest $t_{3}\in \{t_{1},\dots,t_{2}-1\} $ that meets the reachability requirement $\mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}),t_{2},t_{3}) \intersect F = \emptyset$. Then $(q_{p}(t_{3}),t_3)$ is added to $V_{p}$. Finally, we set $t_{0}\leftarrow t_{1}$, $t_{2}\leftarrow t_{3}$ and repeat the same process. The search is stopped when $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \intersect F = \emptyset$ or $t_{0}>t_{2}$. A toy example is shown in \cref{fig:checkpoint-generate}. }
